Articles of Association of London Hackspace Ltd

### 2015-12-01 constitution/articles-body.tex
Remove "No Further Places" wording for elections
Fixes #4
Remove reference to annual general meeting
Fixes #3

\section{Directors Elections}
\item
  \begin{enumerate}
    \item Directors elections must be called by the Board
      \begin{enumerate}
        \item in the case of the first election: before the end of the calendar year following
                the year in which the association was created.
        \item in the case of subsequent elections: before the end of the calendar year following
                the year in which the last election was held.
      \end{enumerate}
    \item
      The directors election must be carried out by electronically polling the membership as follows:
      \begin{enumerate}
        \item The Meek STV voting method with a "no further places" candidate must be used.
        \item All members of the association at the time the election commences are eligible to vote.
        \item The voting period of the election must be no less than 14 days and no more than 28 days.
        \item The quorum of the election must be at least 10\% of eligible voters.
      \end{enumerate}
    \item A director standing for re-election will remain a director until the successful conclusion
          of the election.
    \item A director retiring and not standing for re-election will cease to be a director at the
          start of the election.
    \item Notice of the election must be given at the time the election starts to all members eligible
          to vote who have registered an electronic mail address with the association.
   \end{enumerate}

@@

\item
  \begin{enumerate}
  \item
    The directors may appoint a person who is willing to act to be a
    director.
  \item
    A director appointed by a resolution of the other directors must
    retire at the next annual general meeting and must not be taken
    into account in determining the directors who are to retire by
    rotation.
  \end{enumerate}

>>>>

\section{Directors Elections}
\item
  \begin{enumerate}
    \item Directors elections must be called by the Board
      \begin{enumerate}
        \item in the case of the first election: before the end of the calendar year following
                the year in which the association was created.
        \item in the case of subsequent elections: before the end of the calendar year following
                the year in which the last election was held.
      \end{enumerate}
    \item
      The directors election must be carried out by electronically polling the membership as follows:
      \begin{enumerate}
        \item The Meek STV voting method must be used.
        \item All members of the association at the time the election commences are eligible to vote.
        \item The voting period of the election must be no less than 14 days and no more than 28 days.
        \item The quorum of the election must be at least 10\% of eligible voters.
      \end{enumerate}
    \item A director standing for re-election will remain a director until the successful conclusion
          of the election.
    \item A director retiring and not standing for re-election will cease to be a director at the
          start of the election.
    \item Notice of the election must be given at the time the election starts to all members eligible
          to vote who have registered an electronic mail address with the association.
   \end{enumerate}

@@

\item
  \begin{enumerate}
  \item
    The directors may appoint a person who is willing to act to be a
    director.
  \item
    A director appointed by a resolution of the other directors must
    retire at the next directors election  and must not be taken into
    account in determining the directors who are to retire by rotation.
  \end{enumerate}
